NumPy---Array Programming in Python

### 2020-01-16 body.tex
Minor fixes

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2019scipy},
matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It consists of an $n$-dimensional array object along with utility functions
that operate on it.
Because of its inherent simplicity---being a pointer to memory with some
associated meta-data---the NumPy array is
the {\it de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
{\it Application Programming Interface} (API) has become ubiquitous as
a language for array programming.

@@

@@

Various libraries build on and extend this functionality to further enrich the
ecosystem of available tools.  For example, SciPy adds various mathematical,
scientific, and engineering routines; Pandas provides indexed arrays, known as
dataframes; xarray implements arrays with labeled axes; and Matplotlib
generates publication-ready figures and visualizations.  Employing these
low-level utilities are several widely used technique-specific libraries,
including scikit-learn (machine learning), scikit-image (image processing),
statmodels (statistics),  networkx (graphs and complex networks) \cite{SciPyProceedings_11}, and Napari
(volumetric image visualization).

@@

This culture of using best practices for producing reliable scientific software has been eagerly adopted by the ecosystem of libraries that build on NumPy.  For example, in a recent award given by the Royal Astronomical Society to AstroPy, they state:
\begin{quotation}
\noindent\emph{The Astropy Project has provided hundreds of junior scientists with experience in professional-standard software development practices including use of version control, unit testing, code review and issue tracking procedures. This is a vital skillset for modern researchers that is often missing from formal university education in physics or astronomy.}
\end{quotation}
Community members explicitly work to address this lack of formal education
through formal courses and workshops
\cite{wilson-software-carpentry,hannay-scientific-software-survey,millman2018teaching}.
%\fixme{cite https://scipy-school.org/}.

>>>>

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2019scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It consists of an $n$-dimensional array object along with utility functions
that operate on it.
Because of its inherent simplicity---being a pointer to memory with some
associated meta-data---the NumPy array is
the {\it de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
{\it Application Programming Interface} (API) has become ubiquitous as
a language for array programming.

@@

% - review supporting the ecosystem (actual support element)
%   - docstrings / testing / packaging
%   - coordinating mechanism
%     - deprecation policy

@@

Various libraries build on and extend this functionality to further enrich the
ecosystem of available tools.  For example, SciPy adds various mathematical,
scientific, and engineering routines; Pandas provides indexed arrays, known as
dataframes; xarray implements arrays with labeled axes; and Matplotlib
generates publication-ready figures and visualizations.  Employing these
low-level utilities are several widely used technique-specific libraries,
including scikit-learn (machine learning), scikit-image (image processing),
statsmodels (statistics),  networkx (graphs and complex networks) \cite{SciPyProceedings_11}, and Napari
(volumetric image visualization).

@@

This culture of using best practices for producing reliable scientific software has been eagerly adopted by the ecosystem of libraries that build on NumPy.  For example, in a recent award given by the Royal Astronomical Society to Astropy, they state:
\begin{quotation}
\noindent\emph{The Astropy Project has provided hundreds of junior scientists with experience in professional-standard software development practices including use of version control, unit testing, code review and issue tracking procedures. This is a vital skillset for modern researchers that is often missing from formal university education in physics or astronomy.}
\end{quotation}
Community members explicitly work to address this lack of formal education
through formal courses and workshops
\cite{wilson-software-carpentry,hannay-scientific-software-survey,millman2018teaching}.
%\fixme{cite https://scipy-school.org/}.
